Data Preparation

### 2019-01-10 Data Preparation.Rmd
going back to  previous version

library(gsheet) # import spreadsheets from google drive
library(tm)
library(hunspell) # Stemmer

library(rlist)
#library(tidyr) #(maybe incuded in tidyverse)
#library(tibble)
```

# Import Data
The datasets we use are saved as spreadsheet on our google drive *DARS*. We use the function `gsheet2tbl` to import them to `R Studio` as tibbles. We use the tibble data format (an evolution of the data frame format) because this is the format of reference of the `tidyverse` on whose tools our analysis is heavily based.

@@

### Course Manuals
To expand our topic modeling of course content, we would like to analyse the material in the course manuals. The `corpus_manuals` contains the pdfs of the course manuals for the year 2017-2018 (most recently, available).
```{r}
corpus_manuals <- Corpus(x             = DirSource("Manuals 2017-18"),
                 readerControl = list(reader = readPDF(control = list(text = "-layout"))))
```
## Student Data
The tibble `transcripts` contains the transcripts of a selection of `7` alumni students from the college[^2]. `transcripts` contains information on each course taken by each student such as the receives grade, the semester in which teh course was taken as well as the calendar year.
```{r transcripts}
transcripts <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1kj7tlfJAoN0F7IdoS3saT-2iC3nuDLwnDItNtCKoZ4k/edit#gid=936718979')
print(transcripts)
```

ALL OTHER STUDENTS:
The data we will be using was provided in two documents with the same format. We import them, merge them and remove duplicate rows.

>>>>

library(gsheet) # import spreadsheets from google drive
library(tm)
library(hunspell) # Stemmer
library(rlist)
```

# Import Data
The datasets we use are saved as spreadsheet on our google drive *DARS* (with exeption of grade data saved as csv files on the computer for privacy reasons). We use the function `gsheet2tbl` to import them to `R Studio` as tibbles. We use the tibble data format (an evolution of the data frame format) because this is the format of reference of the `tidyverse` on whose tools our analysis is heavily based.

@@

### Course Manuals
To expand our topic modeling of course content, we would like to analyse the material in the course manuals. The `corpus_manuals` contains the pdfs of the course manuals for the year 2017-2018 (most recently, available).
```{r}
corpus_manuals <- Corpus(x             = DirSource("Manuals 2017-18"),
                 readerControl = list(reader = readPDF(control = list(text = "-layout"))))
```
## Student Data
The tibble `transcripts` contains the transcripts of a selection of `7` alumni students from the college[^2]. `transcripts` contains information on each course taken by each student such as the receives grade, the semester in which the course was taken as well as the calendar year.
```{r transcripts}
transcripts <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1kj7tlfJAoN0F7IdoS3saT-2iC3nuDLwnDItNtCKoZ4k/edit#gid=936718979')
print(transcripts)
```

The data we will be using was provided in two documents with the same format. We import them, merge them and remove duplicate rows.
